A thesis draft

### 2018-11-29 res/sections/08-Background.tex
Minor fixes

\noindent Every NF should be isolated, so that it only has the possibility to
consume a defined set of resources, otherwise the functions running on top of it
could suffer performance degradation~\cite{richart2016resource}. Isolation has
the benefits of offering more security and the possibility to individually
manage the slice~\cite{ordonez2017network}. Slices have to respond to a defined
set o requisites, first of all the possibility to being created by a template,
defined as Network Slice Template (NST). After the NS and the related resources
are created, a NS should be activated. Obviously, for a NS there should be the
possibility to bring changes on-the-fly, and to decommission or deactivate it,
freeing all the occupied resources~\cite{slice20183gpp}.

@@

\noindent The NFV has its own architecture, divided in three main components:
\begin{description}
\item[Virtualized Network Function] that is a software implementation able to fun
  a network function over a NFVI;
\item[NFVI Infrastructure (NFVI)] that includes different physical resources
  and their respective virtualization, that have to support the execution of the
  aforementioned VNFs;
\item[NFV Management and Orchestrator] that has the main role to orchestrate the
  lifecycle of the available resources and of the network functions running on
  top of them.
\end{description}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.7]{etsimano}
  \caption[ETSI NFV MANO framework]{ETSI NFV MANO
    framework~\cite{mijumbi2016management}}
  \label{chap:background:img:etsimano}
\end{figure}

The MANagement and Orchestration (MANO) architecture is divided in turn in three
main components, such as the Virtual Infrastructure Manager (VIM), the VNF
Manager (VNFM) and the NFV Orchestrator (NFVO). The MANO organize and holds
important data, regarding the Network Service (NS) catalog, the list of the VNFs
definitions (VNF catalog) and the current NFV instances and the NFVI resources.

@@

\paragraph{VIM}
As we can see from the Figure~\ref{chap:background:img:etsimano}, it is possible
to denote the position of this component in the schema. The VIM has the role to
communicate with the NFV infrastructure, and to control its physical and virtual
resources. A VIM should has the possibility to control one or more of NFVI. In
general a VIM can be in charge of control a defined set of
NFVI~\cite{mijumbi2016management}

@@

\paragraph{Data Repositories}
Data repositories can be seen as a sort of databases, holding information about
the VNF definitions, the VNF instances with the respective lifecycle status, and
list of the Network Services defined and the resources available and occupied of
the NFVI.

@@

\paragraph*{Service Function}
A single element of an SFC is called Service Function (SF), and its duty is to
elaborate the packets incoming and to forward them to the next receiver. SFs, as
for NFs, can be virtualized or be a set of hardware functions. SF does not
necessary know its part of a chain, and this defines it as SFC unaware or, on
the contrary, SFC aware.

>>>>

\noindent Every NF should be isolated, so that it only has the possibility to
consume a defined set of resources, otherwise the functions running on top of it
could suffer performance degradation~\cite{richart2016resource}. Isolation has
the benefits of offering more security and the possibility to individually
manage the slice~\cite{ordonez2017network}. Slices have to respond to a defined
set of requisites, first of all the possibility to being created by a template,
defined as Network Slice Template (NST). After the NS and the related resources
are created, a NS should be activated. Obviously, for a NS there should be the
possibility to bring changes on-the-fly, and to decommission or deactivate it,
freeing all the occupied resources~\cite{slice20183gpp}.

@@

\noindent The NFV has its own architecture, divided in three main components:
\begin{description}
\item[Virtualized Network Function] that is a software implementation able to
  run a network function over a NFVI;
\item[NFVI Infrastructure (NFVI)] that includes different physical resources
  and their respective virtualization, that have to support the execution of the
  aforementioned VNFs;
\item[NFV Management and Orchestrator] that has the main role to orchestrate the
  lifecycle of the available resources and of the network functions running on
  top of them.
\end{description}

@@

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.8]{etsimano}
  \caption[ETSI NFV MANO framework]{ETSI NFV MANO
    framework~\cite{mijumbi2016management}}
  \label{chap:background:img:etsimano}
\end{figure}

The MANagement and Orchestration (MANO) architecture is divided in turn in three
main components, such as the Virtual Infrastructure Manager (VIM), the VNF
Manager (VNFM) and the NFV Orchestrator (NFVO). The MANO organizes and holds
important data, regarding the Network Service (NS) catalog, the list of the VNFs
definitions (VNF catalog), the current NFV instances and the NFVI resources.

@@

\paragraph{VIM}
As we can see from the Figure~\ref{chap:background:img:etsimano}, it is possible
to denote the position of this component in the schema. The VIM has the role to
communicate with the NFV infrastructure, and to control its physical and virtual
resources. A VIM has the possibility to control one or more of NFVI. In general,
a VIM can be in charge of control a defined set of
NFVI~\cite{mijumbi2016management}

@@

\paragraph{Data Repositories}
Data repositories can be seen as a sort of databases, holding information about
the VNF definitions, the VNF instances with the respective lifecycle status, a
list of the Network Services defined and the resources rispectively available
and occupied of the NFVI.

@@

\paragraph*{Service Function}
A single SFC element is called Service Function (SF), and its duty is to
elaborate the packets incoming and to forward them to the next receiver. SFs, as
for NFs, can be virtualized or be a set of hardware functions. SF does not
necessary know its part of a chain, and this defines it as SFC unaware or, on
the contrary, SFC aware.
